\propertitle

### 2019-07-11 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T14:53:17+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/comparison_marginals.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%comparison_ME_sample_full_levels.nb
But does the application at the full-network level lead to appreciably
different results from that at the sample level? after all we're interested
in an approximate informational sufficiency, not in an analytically exact
one. A correct answer can only be given case by case;
\fig~\ref{fig:comparisons_marginals} gives a graphical answer to this
question in the case of our first data set. The upper plot shows the
maximum-entropy distributions for a full network of $10\,000$ neurons,
constructed from two moments (\textcolor{mygreen}{\textbf{--~--~--}}) and
from four moments (\textcolor{myblue}{\textbf{------}}). The lower plot
shows the maximum-entropy distributions for the sample, from two moments
(\textcolor{mygreen}{$\bm{\triangledown}$}) and from four moments
(\textcolor{myblue}{$\bm{\square}$}), and the distributions obtained by
marginalizing the full-network distribution to the sample size, from two
moments (\textcolor{mygreen}{$\bm{\blacktriangledown}$}) and from four
moments (\textcolor{myblue}{$\bm{\blacksquare}$}). The measured frequency
distribution (\textcolor{myred}{\LARGE$\bm{\bullet}$}) is also shown. We
note the following:
\begin{itemize}
\item The application to the full-network (upper plot) leads to two
  completely different distributions (even different number of modes);
  clearly the two sets of statistics are not even approximately equivalent
  for inferential purposes.
\item The application at the sample level leads to deceivingly similar
  distributions (\textcolor{mygreen}{$\bm{\triangledown}$} and
  \textcolor{myblue}{$\bm{\square}$}), which can only be distinguished on a
  logarithmic scale. This could lead to the erroneous conclusion that the
  two statistics are approximately equivalent.
\item The difference between marginals from the full-network distribution
  and the distributions obtained at the sample level (filled vs empty
  markers) is larger than the difference between different statistics
  (triangles vs squares).
\item The marginals of the application to the full network are closer to
  the measured frequencies than the distributions obtained at the sample
  level (although this closeness is not a valid criterion for their
  goodness).
\end{itemize}
Therefore, the maximum-entropy application at the sample level and at the
full-network level lead to different results; the latter is not only more
meaningful but also superior because it shows clearly the different
informational sufficiency of the two sets of statistics.

@@

The top plots in the figures show the mean
$\int \yF \pf(\yF \| \yD \yI)\,\di\yF$
(\textcolor{myblue}{\textbf{------}}), which is also our belief about the
activity at any single time bin, \eqn~\eqref{eq:probability_AT}, is clearly
different from the maximum-entropy mode. The latter is therefore not a good
approximation for the full density~\eqref{eq:density_proportional}, which
is quite broad, as can be seen from the ten samples
(\textcolor{mygreen}{------}) drawn from it. The mean and the
maximum-entropy mode are nevertheless qualitatively similar. In fact, for
$N=1\,000$ the second peak of the mean is even higher than the
corresponding maximum-entropy one. The samples also show that generally two
main frequency peaks of activity are expected, especially for $N=5\,000$.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-11T15:32:36+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\begin{figure}[!p]
\centering
\includegraphics[width=\linewidth]{_scripts/comparison_full.pdf}%
\\[3em]%
\includegraphics[width=\linewidth]{_scripts/comparison_marginals.pdf}%
\caption{***}
\label{fig:comparisons_marginals}
\end{figure}
%comparison_ME_sample_full_levels.nb
But does the application at the full-network level lead to appreciably
different results from that at the sample level? after all we're interested
in an approximate informational sufficiency, not in an analytically exact
one. A correct answer can only be given case by case;
\fig~\ref{fig:comparisons_marginals} gives a graphical answer to this
question in the case of our first data set. The upper plot shows the
maximum-entropy distributions for a full network of $10\,000$ neurons,
constructed from two moments (\textcolor{mygreen}{\textbf{--~--~--}}) and
from four moments (\textcolor{mypurpleblue}{\textbf{------}}). The lower plot
shows the maximum-entropy distributions for the sample, from two moments
(\textcolor{mygreen}{$\bm{\triangledown}$}) and from four moments
(\textcolor{mypurpleblue}{$\bm{\square}$}), and the distributions obtained by
marginalizing the full-network distribution to the sample size, from two
moments (\textcolor{mygreen}{$\bm{\blacktriangledown}$}) and from four
moments (\textcolor{mypurpleblue}{$\bm{\blacksquare}$}). The measured frequency
distribution (\textcolor{myred}{\LARGE$\bm{\bullet}$}) is also shown. We
note the following:
\begin{itemize}
\item The application to the full-network (upper plot) leads to two
  completely different distributions (even different number of modes);
  clearly the two sets of statistics are not even approximately equivalent
  for inferential purposes.
\item The application at the sample level leads to deceivingly similar
  distributions (\textcolor{mygreen}{$\bm{\triangledown}$} and
  \textcolor{mypurpleblue}{$\bm{\square}$}), which can only be distinguished on a
  logarithmic scale. This could lead to the erroneous conclusion that the
  two statistics are approximately equivalent.
\item The difference between marginals from the full-network distribution
  and the distributions obtained at the sample level (filled vs empty
  markers) is larger than the difference between different statistics
  (triangles vs squares).
\item The marginals of the application to the full network are closer to
  the measured frequencies than the distributions obtained at the sample
  level (although this closeness is not a valid criterion for their
  goodness).
\end{itemize}
Therefore, the maximum-entropy application at the sample level and at the
full-network level lead to different results; the latter is not only more
meaningful but also superior because it shows clearly the different
informational sufficiency of the two sets of statistics.

@@

The top plots in the figures show the mean
$\int \yF \pf(\yF \| \yD \yI)\,\di\yF$
(\textcolor{mypurpleblue}{\textbf{------}}), which is also our belief about the
activity at any single time bin, \eqn~\eqref{eq:probability_AT}, is clearly
different from the maximum-entropy mode. The latter is therefore not a good
approximation for the full density~\eqref{eq:density_proportional}, which
is quite broad, as can be seen from the ten samples
(\textcolor{mygreen}{------}) drawn from it. This broadness is not
surprising: we're making guesses about thousands of neurons from the
observation of fewer than 100. Yet, the mean and the maximum-entropy mode
are qualitatively similar. In fact, for $N=1\,000$ the second peak of the
mean is even higher than the corresponding maximum-entropy one. The samples
also show that generally two high-frequency regions of activity are
expected, especially for $N=5\,000$.

The bottom plots in the figures show our belief distributions for the
marginal frequency of each activity level, $\pf(\yFF_{\yA} \| \yD \yI)$,
with the averages (\textcolor{mypurpleblue}{\textbf{------}}), medians
(\textcolor{mygreen}{\textbf{--~--~--}}), and 16\% and 84\% quantiles
(\textcolor{myyellow}{$\bm{\cdot \cdot \cdot \cdot}$} corresponding to one
standard deviation for a normal distribution).
